%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Pangloss: Testing the reconstruction paper
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[useAMS,usenatbib]{mn2e}
%% letterpaper
%% a4paper

% \voffset=-0.8in

% Packages:
\input psfig.sty
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}

% Macros:
\input{macros.tex}
\input{addresses.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title[Line of Sight Mass Reconstruction]
{Inferring Lensing Mass in the Universe \\
from Photometric Catalog Data}
    
\author[Collett \etal]{%
  Thomas~E.~Collett$^{1}$\thanks{\collettemail},
  Philip~J.~Marshall$^{2}$,
  Matthew~W.~Auger$^{1}$,
  Stefan~Hilbert$^{3}$,
\newauthor{%
  Sherry~H.~Suyu$^{4}$,
  Zachary~Greene$^{4}$,
  Tommaso~Treu$^{4}$\thanks{\packard},
  Christopher~D.~Fassnacht$^{5}$,}
\newauthor{%
  L\`eon~V.~E.~Koopmans$^{6}$,
  Roger~D.~Blandford$^{3}$} 
  \medskip\\
  $^1$\ioa\\
  $^2$\oxford\\
  $^3$\kipac\\
  $^4$\ucsb\\
  $^5$\davis\\
  $^6$\kapteyn
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
             
\date{to be submitted to MNRAS}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}\pubyear{2012}

\maketitle           

\label{firstpage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract} 
abstract
\end{abstract}

% Full list of options at http://www.journals.uchicago.edu/ApJ/instruct.key.html

\begin{keywords}
  gravitational lensing   --
  methods: statistical    --
  galaxies: halos         --
  gaaxies: mass function  --
  cosmology: observations
\end{keywords}

\setcounter{footnote}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
\todo{Phil,(+ Tom)}{Update introduction to reflect the scope of this paper}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Theoretical Background}
\label{sec:theory}
\todo{Phil,(+ Tom)}{Modify the current theory section, emphasiszing how $\kappax$ effects inferred parameters. Justify how we combine individual $\kappa$s to give a total $kappah$ - note that this is the weak lensing limit.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Estimating external convergence: The halo model approximation}
\label{sec:model}

\subsection{Ray-tracing through simulated Lines of Sight}
\label{subsec:raytracing}
\todo{Stefan}{Write section on how the ray tracing was done}

\subsection{Generating mock lightcones from simulations}
\todo{Stefan}{Write section on how halos are extracted from the MS n-body particles}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 

\subsection{Halos}
\label{subsec:halos}
\todo{Tom,Phil}{Check}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 

\subsection{Calibration: Recovering the global $\pr(\kappax)$ using a void correction}
\label{subsec:voids}

\todo{tom}{Outline _EXPLICITLY_ the proceedure we use to correct for voids etc}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Testing the halo model approximation with known halo mass and redshift}
\label{sec:knownMh+z} 

\subsection{How does $\kappah$ relate to $\kappax$?}
Done?
\subsubsection{How does $\gammah$ relate to $\gammax$?}
\todo{tom}{do}
\subsection{Does converting from $\kappah$ to $\kappax$ work?}
\todo{tom}{do}

\subsection{Where does $\kappah$ come from?}
\todo{tom}{do}
\subsubsection{Magnitude}
\subsubsection{Distance}
\subsubsection{Redshift}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Applying the Halo Model approximation to mock catalogs}
\label{sec:obsMstar+z}
\todo{tom}{redo - using new Mhalo-Mstar code}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Testing for Systematic errors}
\todo{tom}{do}
\subsection{Using the wrong M$_{\rm halo}$-M$_{*}$ relation}
\subsection{Selecting bias from a subset of lines of sight?}
\subsubsection{Selecting only the lines of sight with tight $\pr(\kappax)$}
\subsubsection{Selecting only high shear lines of sight}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Discussion}
\label{sec:discuss}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusions}
\label{sec:conclude}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Acknowledgments}
 
TC thanks Vasily Belokurov for guidance and discussions.
We thank Risa Wechsler and Peter Behroozi for useful discussions and 
suggestions.
\input{acknowledgments.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  APPENDICES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendix

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Inferring $\Mhalo$ given a noisy measurement of $\Mstarobs$}
\label{appendix:MSMH}

\todo{Phil}{Check that what's written is correct}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  REFERENCES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% MNRAS does not use bibtex, input .bbl file instead. 
% Generate this in the makefile using bubble script in scriptutils:

% bubble -f paper-lcr.tex references.bib 
% \input{paper-lcr.bbl}

% \bibliographystyle{apj}
% \bibliography{references}

\input{references.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\label{lastpage}
\bsp

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
